ms_results

### 2023-01-08 ms_results.Rmd
updates ahead of circulating among coauthors

@@

Since 1996, nearly all regional trade pairs increased, other than South America. The largest increases occurred for X, Y and Z. At the country level, X% of trade pairs increased, with the most increases for marine/inland aquaculture/capture. The declining exports from South America mirror declining marine catch over this period. [Suggestions for discussion points and context related to this?].

>>>>

```{r LDC_patterns}
# LDC countries according to UN (https://www.un.org/development/desa/dpad/least-developed-country-category/ldcs-at-a-glance.html)
LDC_countries <- c("Afghanistan", "Angola", "Bangladesh", "Benin", "Bhutan", "Burkina Faso", "Burundi", "Cambodia", "Central African Republic", "Chad", "Comoros", "Democratic Republic of the Congo", "Djibouti", "Eritrea", "Ethiopia", "Gambia", "Guinea", "Guinea-Bissau", "Haiti", "Kiribati", "Lao People’s Dem. Republic", "Lesotho", "Liberia", "Madagascar", "Malawi", "Mali", "Mauritania", "Mozambique", "Myanmar", "Nepal", "Niger", "Rwanda", "Sao Tome and Principe", "Senegal", "Sierra Leone", "Solomon Islands", "Somalia", "South Sudan", "Sudan", "Timor-Leste", "Togo", "Tuvalu", "Uganda", "United Republic of Tanzania", "Yemen", "Zambia")

LDC_countries <- countrycode(LDC_countries, origin = "country.name", destination = "iso3c")

ldc_habitat_method_summary <- bilateral_habitat_method_summary %>%
  mutate(
    importer_ldc = case_when(
    (importer_iso3c %in% LDC_countries) ~ "LDC",
    !(importer_iso3c %in% LDC_countries) ~ "non-LDC"),
     exporter_ldc = case_when(
    (exporter_iso3c %in% LDC_countries) ~ "LDC",
    !(exporter_iso3c %in% LDC_countries) ~ "non-LDC")) %>%
  group_by(year, exporter_ldc, importer_ldc, habitat_method) %>%
  summarise(live_weight_t = sum(live_weight_t))

ldc_net_habitat_method_summary <- ldc_habitat_method_summary %>%
  ungroup() %>% 
  filter(importer_ldc == "LDC", exporter_ldc == "non-LDC") %>% 
  select(year, habitat_method, "ldc_import" = "live_weight_t") %>%
  left_join(ldc_habitat_method_summary %>%
              ungroup() %>%
              filter(importer_ldc == "non-LDC", exporter_ldc == "LDC") %>% 
              select(year, habitat_method, "ldc_export" = "live_weight_t"),
            by = c("year", "habitat_method")) %>%
  mutate(net_import = ldc_import-ldc_export,
         net_export = ldc_export-ldc_import)

ldc_net_habitat_method_summary %>%
  filter(habitat_method != "unknown") %>%
  ggplot(aes(x = year, y = net_export/1000000, color = habitat_method)) +
  geom_line() +
  scale_color_manual(values = habitat_source_colors) +
  labs(x = "", y = "Net export (million t)", color = "") +
  theme_minimal() +
  theme(legend.position = "bottom")

ldc_net_habitat_method_summary %>%
  group_by(year) %>% 
  summarise(net_export = sum(net_export))

Since 1996, nearly all regional trade pairs increased, other than South America to Europe and Asia and within North America. The largest average annual growth increases occurred for trade within Asia, within Europe and between Europe and Asia. At the country level, `r round(percent_flow_increases, 1)`% of trade pairs increased, with the most increases for marine/inland aquaculture/capture. The declining exports from South America mirror declining marine catch over this period. [Suggestions for discussion points and context related to this?].

@@
